\documentclass{article}

% Packages
\usepackage{titlesec}
\usepackage{titling}
\usepackage[left=1in, right=1in, top=0.5in, bottom=1in]{geometry} % This is the margins
\usepackage{hyperref}

% Section styling
\titleformat{\section}
{\huge}
{}
{0em}
{\bfseries}[\titlerule]

% Section spacing
\titlespacing{\section}
{0em}
{1em}
{0.5em}

% Subsection styling
\titleformat{\subsection}
{\large}
{}
{0.2em}
{\bfseries}

% Subsection spacing
\titlespacing{\subsection}
{0em}
{0.25em}
{0.25em}

% Remove page nums
\pagestyle{empty}

% Title stlying and format
\renewcommand{\maketitle}{
\begin{center}
{\huge \bfseries \theauthor}

\vspace{0.25em}
\url{mcraealex.github.io} | \url{github.com/mcraealex} | \href{mailto:mail@alexandermcrae.com}{mail@alexandermcrae.com}
\end{center}}

% Colored Urls
\newcommand{\hrefColored}[3]{\href{#2}{\color{#1}{#3}}}

% Hyperlinks styleing
\hypersetup{
    colorlinks,
    linkcolor=blue
}

\begin{document}

\title{R\'esum\'e}
\author{Alexander McRae}

\maketitle

\section{Education}

\noindent University of Victoria \hfill September 2017 - present\\
\textit{Bachelor of Science in Computer Science, Minor in Business}

\section{Relavent Skills}

\subsection{Programming Langauges}

Rust, C/C++, Go, Elixir, Python

\subsection{Web Developement}

Typescript, React, Vue, Nodejs, SQL, Webpack

\subsection{Graphics}

Ray Tracing, Vulkan, OpenGL, WebGL

\section{Experience}

\subsection{3D Programmer at \hrefColored{blue}{https://www.suntrackertech.com}{Suntracker Technologies Ltd.} (Sept 2019 - April 2020)}

Developed an embeded 3D rendering engine from scratch using OpenGL. Participated
in Illumination Engineering Society talks and meetings. Worked the first 4 
months as a co-op student and then continued as a contractor.

\subsection{Campus Ambassador at \hrefColored{blue}{https://play.battlesnake.com/}{BattleSnake} (Jan 2020 - Current)}

Create student involvement and interest in the open source project BattleSnake.
Organized and hosted a tournament where new students came and learned about the 
basics of BattleSnake. Helped participants create their snakes for the tournament at the end of
the day. Create new starter snakes (templates) which allow people to get up and 
running quickly with BattleSnake in various languages.

\section{Projects}

\subsection{GumShoe \href{https://github.com/McRaeAlex/Connector/tree/main/gumshoe}{github.com/McRaeAlex/Connector/tree/main/gumshoe}}

A bug tracker developed with my HTTP library. It is used to track bugs for itself as well as the underlying HTTP library.

\subsection{Connector \href{https://github.com/McRaeAlex/Connector}{github.com/McRaeAlex/Connector}}

Created a HTTP library/framework which allows for composable middleware, easy testing and high performance. Currently used in GumShoe as it's HTTP layer.

\subsection{Pipe Operator \href{https://github.com/McRaeAlex/pipe-op}{github.com/McRaeAlex/pipe-op}}

Developed a Rust library which uses meta programming to bring the functionality of the Elixir pipe operator to Rust.

\subsection{Ray Tracer \href{https://github.com/McRaeAlex/tiny-raytracer}{github.com/McRaeAlex/tiny-raytracer}}

Implemented a extensible rendering engine with lighting, reflection, and 
refraction.

\subsection{Tiny URL \href{https://github.com/McRaeAlex/tinyURL}{github.com/McRaeAlex/tinyURL}}

Developed a URL compressor similar to \href{bit.ly}{bit.ly}, which can be used to share long links with a 
shorter URL.

\subsection{Vancouver CSS  \href{https://github.com/McRaeAlex/VancouverCSS}{github.com/McRaeAlex/VancouverCSS}}

Created a CSS animation created to learn about some advanced features of CSS and to be 
used as the background of my website. Checkout the website.\\
\indent Website: \href{https://mcraealex.github.io/VancouverCSS/}{mcraealex.github.io/VancouverCSS}

\end{document}