\documentclass{article}

% Packages
\usepackage{titlesec}
\usepackage{titling}
\usepackage[left=1in, right=1in, top=0.5in, bottom=1in]{geometry} % This is the margins
\usepackage{hyperref}
\usepackage{enumitem}

% Section styling
\titleformat{\section}
{\huge}
{}
{0em}
{\bfseries}[\titlerule]

% Section spacing
\titlespacing{\section}
{0em}
{1em}
{0.5em}

% Subsection styling
\titleformat{\subsection}
{\large}
{}
{0.2em}
{\bfseries}

% Subsection spacing
\titlespacing{\subsection}
{0em}
{0.25em}
{0.25em}

% Remove page nums
\pagestyle{empty}

% Title stlying and format
\renewcommand{\maketitle}{
\begin{center}
{\huge \bfseries \theauthor}

\vspace{0.25em}
\url{mcraealex.github.io} | \url{github.com/mcraealex}
\href{mailto:mail@alexandermcrae.com}{mail@alexandermcrae.com} | \href{https://linkedin.com/in/mcraealex}{linkedin.com/in/mcraealex}
\end{center}}

% Colored Urls
\newcommand{\hrefColored}[3]{\href{#2}{\color{#1}{#3}}}

% Hyperlinks styleing
\hypersetup{
    colorlinks,
    linkcolor=blue
}

\begin{document}

\title{R\'esum\'e}
\author{Alexander McRae}

\maketitle

\section{Education}

\noindent University of Victoria \hfill September 2017 - present\\
\textit{Bachelor of Science in Computer Science, Minor in Business}

\section{Relavent Skills}

\subsection{Programming Langauges}

Rust, C/C++, Go, Elixir, JavaScript, Bash, C\#, Awk

\subsection{Web Developement}

Typescript, React, Vue, Nodejs, SQL, Webpack

\subsection{Other}

Git, SQL, Docker, Linux, RISC-V, Vulkan

\section{Experience}

\subsection{3D Programmer at \hrefColored{blue}{https://www.suntrackertech.com}{Suntracker Technologies Ltd.} (Sept 2019 - April 2020)}

Developed an embeded 3D rendering engine from scratch using OpenGL. Participated
in Illumination Engineering Society talks and meetings. Worked the first 4 
months as a co-op student and then continued as a contractor.

\subsection{Campus Ambassador at \hrefColored{blue}{https://play.battlesnake.com/}{BattleSnake} (Jan 2020 - Current)}

Create student involvement and interest in the open source project BattleSnake.
Organized and hosted a tournament where new students came and learned about the 
basics of BattleSnake. Helped participants create their snakes for the tournament at the end of
the day. Create new starter snakes (templates) which allow people to get up and 
running quickly with BattleSnake in various programming languages.

\section{Projects}

\subsection{MobilityFirst: Connection Upgrade Protocol \href{https://mcraealex.github.io/research/csc466}{mcraealex.github.io/research/csc466}}

\begin{itemize}
    \item Created a protocol and programming interface for creating sockets which allow for peers to migrate to different networks and change IP addresses without losing connections.
\end{itemize}

\subsection{AlpineToast: Npm package to create toasts \href{https://github.com/McRaeAlex/AlpineToast}{github.com/McRaeAlex/AlpineToast}}

\begin{itemize}
    \item Created an extensible JavaScript library which allows users to create customizable toasts both programmatically and through plain HTML attributes. 
    \item Typescript, Webpack, Rollup, TailWindCSS 
\end{itemize}

\subsection{Village: Social media for small friend groups \href{https://github.com/McRaeAlex/village}{github.com/McRaeAlex/village}}

\begin{itemize}
    \item Developed a social media application which allows users to take control of their social media presence and only share with whom they feel comfortable.
    \item Elixir, Postgresql, Javascript, HTML, CSS, CRUD, Websockets, PubSub, Docker
\end{itemize}

\subsection{Connector: HTTP Framework \href{https://github.com/McRaeAlex/connector}{github.com/McRaeAlex/Connector}}

\begin{itemize}
    \item Designed and implemented a HTTP library, language extension, and example project to better understand how high performance web servers operate.
    \item Rust, HTTP, Async IO
\end{itemize}

\end{document}